### 2014-05-07 sprout_intro.tex
Revise through some of eval

\begin{figure}
\caption{Skype and Sprout on the Verizon LTE downlink trace. For Skype, overshoots in throughput lead to large standing queues. Sprout tries to keep each
packet's delay less than 100~ms with 95\% probability.}
\label{fig:skypevssprout}
\vspace{\baselineskip}
\scriptsize\def\svgwidth{\columnwidth}\input{newfigure1.pdf_tex}
\end{figure}

%\paragraph{Contributions.}
This paper presents {\em Sprout}, a transport protocol designed for
interactive applications on variable-quality networks. Sprout uses the
receiver's observed packet arrival times as the primary signal to
determine how the network path is doing, rather than the packet loss,
round-trip time, or one-way delay. Moreover, instead of the
traditional reactive approach where the sender's window or rate
increases or decreases in response to a congestion signal, the Sprout
receiver makes a short-term forecast (at times in the near future) of
the bottleneck link rate using probabilistic inference.  From this
model, the receiver predicts how many bytes are likely to cross the
link within several intervals in the near future with at least 95\%
probability. The sender uses this forecast to transmit its data,
bounding the risk that the queuing delay will exceed some threshold,
and maximizing the achieved throughput within that constraint.

@@

%\begin{center}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangout & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}
%\end{center}

@@

We also evaluated a simplified version of Sprout, called Sprout-EWMA,
that tracks the network bitrate with a simple exponentially-weighted
moving average, rather than making a cautious forecast of future
packet deliveries with 95\% probability.

@@

\noindent \begin{tabular}{|l|c|c|}
\hline
Protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout-EWMA} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout-EWMA & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.53~s) \\
\hline
Sprout & $2.0\times$ & \cellcolor{red!20}$0.60\times$ (0.32~s) \\
Cubic & $1.8\times$ & $48 \times$ (25~s)\\
\hline
Cubic-CoDel & 1.3 $\times$ & \cellcolor{red!20}$0.95\times$ (0.50~s)\\
\hline
\end{tabular}

@@

The source code for Sprout, our wireless network trace capture
utility, and our trace-based network emulator is available at
\texttt{http://alfalfa.mit.edu/} .
%\texttt{http://github.com/keithw/alfalfa}.

>>>>

\begin{figure}
\caption{Skype and Sprout on the Verizon LTE downlink trace. For Skype, overshoots in throughput lead to large standing queues. Sprout tries to keep each
packet's delay less than 100~ms with 95\% probability.}
\label{fig:skypevssprout}
\vspace{\baselineskip}
\footnotesize\def\svgwidth{\columnwidth}\input{newfigure1.pdf_tex}
\end{figure}

%\paragraph{Contributions.}
This chapter describes Sprout, a transport protocol designed for
interactive applications on variable-quality networks. Sprout uses the
receiver's observed packet arrival times as the primary signal to
determine how the network path is doing, rather than the packet loss,
round-trip time, or one-way delay. Moreover, instead of the
traditional reactive approach where the sender's window or rate
increases or decreases in response to a congestion signal, the Sprout
receiver makes a short-term forecast (at times in the near future) of
the bottleneck link rate using probabilistic inference.  From this
model, the receiver predicts how many bytes are likely to cross the
link within several intervals in the near future with at least 95\%
probability. The sender uses this forecast to transmit its data,
bounding the risk that the queuing delay will exceed some threshold,
and maximizing the achieved throughput within that constraint.

@@

\begin{centering}
\noindent \begin{tabular}{|l|c|c|}
\hline
App/protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.32~s) \\
\hline
Skype & $2.2\times$ & $7.9\times$ (2.52~s) \\
Hangout & $4.4\times$ & $7.2\times$ (2.28~s) \\
Facetime & $1.9\times$ & $8.7\times$ (2.75~s) \\
\hline
Compound & $1.3\times$ & $4.8\times$ (1.53~s) \\
TCP Vegas & $1.1\times$ & $2.1\times$ (0.67~s) \\
LEDBAT & $1.0\times$ & $2.8\times$ (0.89~s) \\
Cubic & \cellcolor{red!20}$0.91\times$ & $79\times$ (25~s)\\
\hline
Cubic-CoDel & \cellcolor{red!20}$0.70\times$ & $1.6\times$ (0.50~s) \\
%CUBIC/CoDel & & \\
%Compound/CoDel & & \\
\hline
\end{tabular}

\end{centering}

@@

We also evaluated a simplified version of Sprout, called Sprout-EWMA,
that estimates the network's future packet-delivery rate with a simple
exponentially-weighted moving average, rather than using its
probabilistic model to make a cautious forecast of future packet
deliveries with 95\% probability.

@@

\vspace{\baselineskip}
\begin{centering}
\noindent \begin{tabular}{|l|c|c|}
\hline
Protocol & Avg.~speedup & Delay reduction \\
& \footnotesize{vs.~Sprout-EWMA} & \footnotesize{(from avg.~delay)}\\
\hline
\hline
\cellcolor{blue!20}Sprout-EWMA & \cellcolor{blue!20}$1.0\times$ & \cellcolor{blue!20}$1.0\times$ (0.53~s) \\
\hline
Sprout & $2.0\times$ & \cellcolor{red!20}$0.60\times$ (0.32~s) \\
Cubic & $1.8\times$ & $48 \times$ (25~s)\\
\hline
Cubic-CoDel & 1.3 $\times$ & \cellcolor{red!20}$0.95\times$ (0.50~s)\\
\hline
\end{tabular}

\end{centering}

@@

The source code for Sprout, our wireless network trace capture
utility, our trace-based network emulator, and instructions to
reproduce the experiments in this chapter are available at
\url{http://alfalfa.mit.edu/} .
%\texttt{http://github.com/keithw/alfalfa}.
